\documentclass[letterpaper,12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{url}

\begin{document}


theme : Privacy increases usability
title?

outline : 


Describe workflow in existing payment systems
- Cash
  - authentication at ATM
  - transaction authenticated by the cash
  - worries : counterfeit bills, wrong currency, etc.
  - refunds
- CC authentication 
  - online vs offline
  - extended verification
  - credential theft
  "this reversal of authentication vs shoping slows shopping"
    - worse because exposing yourself to a merchant
    - can choose not to use a particular ATM
    - 40 million stolen at target
  - refunds, annoys banks
  - swipe vs chip vs NFC
- Bitcoin
  - external application
    - p2p not prowser friendly
  - 5+ or 10 minute transactions mean designing new shopping carts
  - minning suck0rs, 
    - massive transaction fees : blockchain.info 
      - hits you 2-3 times
  - conversion sucks
  - DDoS : wired article?


Taler overview
  copy from proposals?
- bank, mint
- wallet
- merchant
- auditor

Taler payment process from customers prospective
- similar to cash 
  - ATM
  - merchant
- contract 
  - digitally signed is better than paper receipt
- failure modes
  - insufficient funds
  - restoring from backups causes double spending
    - mint gives proof
  - restoring from backups can lose coins
  - mint not accepted by merchant
    - F
- change
- refunds
  vs CC
  vs Cash


Wallet provides isolation
  Near copy from EXIST protosal?
- Limits user risk
- Nearly eliminates risk for merchant and mint
  - lower transaction fees
- Reserves simplify things 

Denomination choice
- Anonymity refresh protocol
- Withdraw automates like ATMs

Browser extension
- RESTful vs Bitcoin, OpenCoin, etc.
  - Retrying RESTful transactions always works
- minimizing dialog
- see & pay ??
- TBB integration
  - Needed anyways
- Other browser integration?
  - Is it wise?  Ok if not worried about anonymity  Taler is still better
  - Is tor2web worse? 
- W3C

Autopay?  pat payment recognision?
- dangerous?
- high charges
- good for funny money

NFC


\end{document}



